---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# omicsTools

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/omicsTools)](https://cran.r-project.org/package=omicsTools)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

The goal of omicsTools is to provide tools for processing and analyzing omics data from genomics, transcriptomics, proteomics, and metabolomics platforms. It provides functions for preprocessing, normalization, visualization, and statistical analysis, as well as machine learning algorithms for predictive modeling. omicsTools is an essential tool for researchers working with high-throughput omics data in fields such as biology, bioinformatics, and medicine.

License: MIT + file LICENSE

## Installation

### CRAN version

You can install the Stable version of omicsTools like so:

```r
install.packages("omicsTools")
```

### Development version

To get a bug fix, or use a feature from the development version, you can install omicsTools from GitHub.
```r
if (!require("devtools", quietly = TRUE))
    install.packages("devtools")
devtools::install_github("YaoxiangLi/omicsTools")
```





## Example

This is a basic example which allows you to start using it:

```{r example}
library(omicsTools)
omicsTools::run_app()
```
To keep `README.md` up-to-date. `devtools::build_readme()`
