---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# omicsTools

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/omicsTools)](https://cran.r-project.org/package=omicsTools)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

The goal of omicsTools is to provide tools for processing and analyzing omics data from genomics, transcriptomics, proteomics, and metabolomics platforms. It provides functions for preprocessing, normalization, visualization, and statistical analysis, as well as machine learning algorithms for predictive modeling. omicsTools is an essential tool for researchers working with high-throughput omics data in fields such as biology, bioinformatics, and medicine.

License: MIT + file LICENSE

## Installation

You can install the development version of omicsTools like so:

``` r
devtools::install_github("https://github.com/YaoxiangLi/omicsTools.git")
```

## Example

This is a basic example which allows you to start using it:

```{r example}
library(omicsTools)
omicsTools::run_app()
```
To keep `README.md` up-to-date. `devtools::build_readme()`
